Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho, and Potential Impacts to Local Chinook Salmon Populations

### 2022-02-23 analysis/paper/paper.Rmd
Incorporated edits from coauthors

Most predation studies have focused on reservoirs [@Murphy2021] and mainstem reaches [@Zimmerman1999; @Tabor1993; @Ward1995; @Shively1996] of the Columbia River basin whereas considerably less is known about the interaction between upstream, river-dwelling piscivorous fishes and their impacts on salmonid recovery above the reservoir systems [@Rubenson2020]. Upstream habitats containing slower water velocities and other attributes that support piscivorous predators may overlap with essential habitat for some salmonid species and life stages. One such example is Deadwater Slough, an approximately `r round(ddw_rkms, 1)` km long reach of unnaturally slow and deep water in the Salmon River, Idaho. The Deadwater Slough contains historically important overwinter rearing habitat for juvenile Chinook Salmon *O. tshawytscha* and is part of the migratory pathway for upstream Chinook Salmon, the endangered Snake River Sockeye Salmon *O. nerka* population [@Axel2015] and several populations of threatened Snake River steelhead. The slough is also inhabited by piscivorous predators, including Northern Pikeminnow and Smallmouth Bass *Micropterus dolomieu* that are potential sources of mortality for these rearing and migrating salmonids.

>>>>

Most predation studies focus on reservoirs [@Murphy2021] and mainstem reaches [@Zimmerman1999; @Tabor1993; @Ward1995; @Shively1996] of the Columbia River basin whereas considerably less is known about the interaction between upstream, river-dwelling piscivorous fishes and their impacts on salmonid recovery above the reservoir systems [@Rubenson2020]. Upstream habitats containing slower water velocities and other attributes that support piscivorous predators may overlap with essential habitat for some salmonid species and life stages. One such example is Deadwater Slough, an approximately `r round(ddw_rkms, 1)` km long reach of unnaturally slow and deep water in the Salmon River, Idaho. The Deadwater Slough contains historically important overwinter rearing habitat for juvenile Chinook Salmon *O. tshawytscha* and is part of the migratory pathway for upstream Chinook Salmon, the endangered Snake River Sockeye Salmon *O. nerka* population [@Axel2015] and several populations of threatened Snake River steelhead. The slough is also inhabited by piscivorous predators, including Northern Pikeminnow and Smallmouth Bass *Micropterus dolomieu* that are potential sources of mortality for these rearing and migrating salmonids.
